SAT-solving Linear Ordered Attribute Grammars

### 2014-10-07 paper/paper.tex
Required latex files (including a messy format.tex)
Add abstract and remove pdf from repo

@@

\begin{abstract}
A nice abstract here.
\keywords{Attribute Grammars, SAT-Solving}
\end{abstract}

@@

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tikz}
\input{./formats.tex}

@@

\begin{abstract}
Attribute grammars are a formalism for describing tree computations (catamorphisms), and are therefore suitable for implementing the semantics of programming languages. A well-known subclass is the class of linear ordered attribute grammars, for which a linear evaluation order can be found statically. The problem of finding such an order is however known to to be NP-hard.

In this paper we encode linear ordered attribute grammar scheduling as a SAT-problem. We encode cycle-freeness of the dependency graphs efficiently by making the graphs chordal, which is a new approach for encoding such graph property in SAT. We show that using Minisat as an external SAT-solver the scheduling algorithm runs much faster than existing scheduling algorithms on real-world examples. Furthermore, this approach allows fine-grained control over the resulting schedule, thereby enabling new attribute grammar optimizations.

\keywords{Attribute Grammars, static analysis, SAT-solving}
\end{abstract}

@@

\section{Linear Ordered Attribute Grammars}
\input{./loags.tex}

\bibliographystyle{splncs}
\bibliography{biblio}
